### 2020-10-08 paper/natastron/methods.tex
Guy & Bill comments

While these two limits cause concern when studying the most extreme rotators, the results presented in this work are data-driven by stars with rotation rates in the regime of 10 to 40 days, and so we do not expect these limits to bias our conclusions.

>>>>

While these two limits cause concern when studying the most extreme rotators, the results presented in this work are driven by stars with rotation rates in the regime of 10 to 40 days. Above, we demonstrated that results on period for these stars were data-driven (i.e. do not reflect the priors), indicating that the splitting is well resolved in this regime, and so we do not expect these limits to bias our conclusions.

### 2020-10-08 paper/natastron/paper.tex
Guy & Bill comments

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
 %500 words
Gyrochronology is the study of the relationship between a star's rotation period and its age. As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing its rotation. Because the loss rate is related to temperature, the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}. As a result, knowing the rotation and colour of a star provides an avenue to measure its age, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}. Age can otherwise be difficult to infer, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.

Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $4\, \rm{Gyr}$ \cite{meibom+2015, barnes+2016}. With the launch of the \textit{Kepler} mission \cite{borucki+2010}, ages of main sequence field stars (i.e. not in clusters) became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}. When looking at these stars, disagreements were found between the observations and gyrochronology beyond the middle of stars' main sequence lifetimes, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}. It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops. This would cause stars to maintain relatively fast rotation rates at old ages, which we would not expect from the extrapolation of existing gyrochronology relations.

The mechanism by which weakened magnetic braking occurs has since been the subject of ongoing debate, and may be connected to changes in the magnetic field morphology \cite{vansaders+2016,reville+2015,garraffo+2016, metcalfe+2016, metcalfe+2019, see+2019}. It may also be explained from an observational point of view. A large scale survey of stellar rotation rates measured using star-spots pointed out a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}. As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015, reinhold+2020}. The point at which the detection probability drops appears to lie at a similar level of activity as the expected onset of weakened magnetic braking, pitting these two possibilities against one another \cite{vansaders+2019}.

Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new measurements of rotation in quiescent stars, which can be provided by asteroseismology. A star's rotation causes modes of oscillation to split into multiplets, making it possible to obtain an independent rate of rotation by measuring the splitting between oscillation frequencies \cite{ledoux1951}. Asteroseismic rotation requires a faster observing cadence and higher signal-to-noise than than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues. This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence. Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and evaluated this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\

>>>>

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
 %500 words
Gyrochronology is the study of the relationship between a star's rotation period and its age. As a star grows older along the main sequence, magnetic winds will cause it to lose angular momentum, slowing its rotation. The loss rate is thought to depend on the depth of the convection zone, which is a strong function of mass and temperature, and so the rotation period of a young star will rapidly settle on to a plane in age-colour-rotation space \cite{barnes2007}. Knowing the rotation and colour of stars therefore provides an avenue to measure ages, to a precision of $\sim 10\%$ for stars most similar to the Sun \cite{meibom+2015}. Age can otherwise be difficult to infer, and so gyrochronology enables more in-depth studies of stellar populations and individual stars \cite{leiner+2019,claytor+2019}.

Gyrochronology was previously calibrated on stellar clusters, which have well constrained ages, but only up to roughly $4\, \rm{Gyr}$ \cite{meibom+2015, barnes+2016}. Recently, ages of main sequence field stars (i.e. not in clusters) observed by \kepler \cite{borucki+2010} became more widely available through asteroseismology, the study of stellar variability \cite{silvaaguirre+2015}. When looking at these stars, disagreements were found between the observations and gyrochronology beyond the middle of stars' main sequence lifetimes, which could not be reconciled with existing theories \cite{angus+2015, nielsen+2015, davies+2015}. It was proposed that at some stage in a star's evolution it undergoes \textit{weakened magnetic braking} (WMB, \cite{vansaders+2016}), where the efficiency of angular momentum loss rapidly drops. This would cause stars to maintain relatively fast rotation rates at old ages, which we would not expect from the extrapolation of existing gyrochronology relations.

The mechanism by which weakened magnetic braking occurs is subject of debate, and may be connected to changes in the magnetic field morphology \cite{vansaders+2016,reville+2015,garraffo+2016, metcalfe+2016, metcalfe+2019, see+2019}. It may also be explained from an observational point of view. A large survey of stellar rotation rates measured using star-spots found a lack of slowly rotating stars older then Sun \cite{mcquillan+2014}. As activity reduces with age, older stars with fewer star-spots are less likely to have their rotation measured \cite{matt+2015, reinhold+2020}. The point at which the detection probability drops appears to lie at a similar level of activity as the expected onset of weakened magnetic braking, placing these two possibilities in opposition to one another \cite{vansaders+2019}.

Determining whether weakened magnetic braking is a true phenomenon or a bias in star-spot observations requires new measurements of rotation in quiescent stars, which can be provided by asteroseismology. A star's rotation causes modes of oscillation to split into multiplets, enabling measurement of independent rotation rates by measuring the rate of splitting \cite{ledoux1951}. Asteroseismic rotation requires a faster observing cadence and higher signal-to-noise than spot rotation, but does not require spots to be visible, meaning that we can measure rotation for older, quiescent stars that would not have been present in existing rotation catalogues. This makes asteroseismic rotation rates a perfect test of weakened magnetic braking on the main sequence. Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of  ages, and determined whether this new ensemble agrees more closely with a classical rotational evolution scenario, or one in which weakened magnetic braking takes place.\\
